What's in a Domain? Anaylsis of URL Features

### 2022-09-19 paper/paper.tex
References cleanup and intro/lit review

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{What's in a Domain?: Feature Engineering for URLs}

@@

Multiple data science and machine learning applications on internet data 
Write a literature review \cite{Vazhayil2018}
\cite{Canali2011}
\cite{Ayes2019}
\cite{Mamun2016}
\cite{Li2020}
\cite{Basnet2012}
\cite{Basnet2014}
\cite{Tupsamudre2019}
\cite{Le2018}
\cite{Baykan2009}
\cite{Kan2005}
\cite{Hernandez2012}
\cite{Chung2022}
\cite{Qiu2020}
\cite{Vaishnavi2021}
\cite{Xu2021}
\cite{Rhea2022}

Common approaches to feature engineering on URLs include string matching and regular expressions to
identify key sequences \cite{}, generation of task specific embedding vectors\cite{Qiu2020} and the
usage of domain name servers or registrars for ancillary information \cite{}

@@

>>>>

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{What's in a Domain? Anaylsis of URL Features}

@@

Multiple data science and machine learning applications on internet data 
Write a literature review \cite{Vazhayil2018}
\cite{Canali2011}
\cite{Ayes2019}
\cite{Mamun2016}
\cite{Li2020}
\cite{Basnet2012}
\cite{Basnet2014}
\cite{Tupsamudre2019}
\cite{Le2018}
\cite{Baykan2009}
\cite{Kan2005}
\cite{Hernandez2012}
\cite{Chung2010}
\cite{Qiu2020}
\cite{Vaishnavi2021}
\cite{Xu2021}
\cite{Rhea2022}

Common approaches to feature engineering on URLs include string patterns and regular expressions to
identify key sequences \cite{}, n-gram models \cite{Baykan2009}, 
the generation of task specific embedding vectors\cite{Qiu2020} and the
usage of domain name servers or registrars for ancillary information \cite{}

@@

4 Universities data http://www.cs.cmu.edu/afs/cs.cmu.edu/project/theo-20/www/data/
